```{r}
aussies <- read.csv("~/Desktop/aussies.csv")
```

create training dataset and test dataset

```{r}
samp <- sort (sample(1:202, 101))
aussies.train <- aussies[samp,]
aussies.test <- aussies[-samp,]
```

fit the linear regression model 

```{r}
lmWt.fit <- lm(Wt~ Sex+as.factor(SportN), data = aussies.train)
summary(lmWt.fit)
coef(lmWt.fit)
```

generate MSE predictions for linear model 

```{r}
ypred.lm <- predict(lmWt.fit, aussies.test)
View (ypred.lm)
MSE.lm <- mean ((aussies.test$Wt - ypred.lm) ^2)
```

fit lasso

```{r}
library (glmnet)
dummy.train <- model.matrix(~aussies.train$Sport-1)
x.train <- cbind (aussies.train$Sex, dummy.train)
y.train <- data.matrix(aussies.train$Wt) 
lmWt.la <- glmnet(x.train,y.train,alpha=1)
```

generate MSE predictions for lasso

```{r}
dummy.test <- model.matrix(~aussies.test$Sport-1)
x.test <- cbind (aussies.test$Sex, dummy.test)
ypred.la <- predict(lmWt.la, x.test, s = 0.01)
MSE.la <- mean ((aussies.test$Wt - ypred.la) ^2)
```

fit group lasso

```{r}
library(gglasso)
group <- c (1, rep(2,10))
lmWt.gg <- gglasso(x.train,y.train, dfmax = 5, group)
```

generate MSE predictions for group lasso

```{r}
ypred.gg <- predict(lmWt.gg, x.test, s = 0.01)
MSE.gg <- mean ((aussies.test$Wt - ypred.gg) ^2)
```

compare MSE

```{r}
MSE.lm 
MSE.la
MSE.gg
```

generate LOOCV cross validations for linear model

```{r}
library (boot)
glmWt <- glm(Wt~ Sex+as.factor(SportN), data = aussies)
cv.errlm=cv.glm(aussies,glmWt)
CV.lm <- cv.errlm$delta[1]
```

generate LOOCV cross validations for lasso model 

```{r}
dummy <- model.matrix(~aussies$Sport-1)
x <- cbind (aussies$Sex, dummy)
y <- data.matrix(aussies$Wt)
cv.errla = cv.glmnet(x,y,alpha=1)
numla <- which(cv.errla$lambda == cv.errla$lambda.min)
CV.la <- cv.errla$cvm[numla]
```

generate LOOCV cross validations for grouped lasso model 

```{r}
dummy <- model.matrix(~aussies$Sport-1)
x <- cbind (aussies$Sex, dummy)
y <- data.matrix(aussies$Wt)
group <- c (1, rep(2,10))
cv.errgg = cv.gglasso(x,y,group,nfolds = nrow(aussies))
numgg <- which(cv.errgg$lambda == cv.errgg$lambda.min)
CV.gg <- cv.errgg$cvm[numgg]
```

compare MSE-LOOCV

```{r}
CV.lm
CV.la
CV.gg
```

generate K-fold CV for linear model 

```{r}
library (boot)
glmWt <- glm(Wt~ Sex+as.factor(SportN), data = aussies)
cv.errlm10=cv.glm(aussies,glmWt, K = 10)
CV.lm10 <- cv.errlm10$delta[1]
```

generte K-fold CV for lasso model 

```{r}
dummy <- model.matrix(~aussies$Sport-1)
x <- cbind (aussies$Sex, dummy)
y <- data.matrix(aussies$Wt)
cv.errla10 = cv.glmnet(x,y,alpha=1,nfolds = 10)
numla10 <- which(cv.errla10$lambda == cv.errla10$lambda.min)
CV.la10 <- cv.errla10$cvm[numla10]
```

generate K-fold for grouped lasso model

```{r}
dummy <- model.matrix(~aussies$Sport-1)
x <- cbind (aussies$Sex, dummy)
y <- data.matrix(aussies$Wt)
group <- c (1, rep(2,10))
cv.errgg10 = cv.gglasso(x,y,group,nfolds = 10)
numgg10 <- which(cv.errgg10$lambda == cv.errgg10$lambda.min)
CV.gg10 <- cv.errgg10$cvm[numgg10]
```

compare MSE-K-fold

```{r}
CV.lm10
CV.la10
CV.gg10
```

